Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-11 WRITEUP/ms.tex
minor text edit

Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in Figures~\ref{fig:Q}, \ref{fig:Qstar}, and \ref{fig:Qeff}, respectively (see \Fig{h2density} for an example of MCs identified 
in this snapshot). Fragmentation are expected in regions of low Toomre $Q$ values.
Further interpretation and implication of this is discussed in \Sec{origin}.

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_gas_toomre_proj_0_zoom_2.0_kpc}.png}
\caption{
Maps of the total gas surface density (top left), 
velocity dispersion (top right),
epicyclic frequency (bottom left), 
and Toomre $Q$ parameter (bottom right) in the $xy$-plane.
Modest smoothing has been applied to the maps. 
A divergent colormap is used for the Toomre $Q$ map to facilitate 
identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
Crosses correspond to positions of MCs identified using the lowest $n_{\rm cut}$. % using 0.32
Positions of sub-MCs are not shown (but see top row of \Fig{Qeff} for an example). 
\label{fig:Q}}
\addtocounter{figure}{-1}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=10 0 100 20, clip, width=0.35\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_0.32}.png}
\includegraphics[trim=30 0 10 20, clip, width=0.425\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_6.81}.png}  \\
\includegraphics[trim=10 0 0 10, clip, width=0.425\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_2.0_kpc}.png} \\
\includegraphics[trim=30 25 30 20, clip, width=0.4\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_0.8_kpc_6.81}.png}
\includegraphics[trim=10 0 0 0, clip, width=0.38\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_0.8_kpc}.png}
\caption{
Effective two-component Toomre $Q_{\rm eff}$ (top row) 
and gas surface density (middle) maps projected onto the $xy$-plane.
Positions of MCs identified using the lowest $n_{\rm cut}$\eq0.32\,cm$^{-3}$ (top left; same as \Fig{Q})
and $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (top right) are overplotted as crosses.
Bottom row: Effective $Q_{\rm eff}$ (left) and gas surface density (right) maps zoomed in on the central 1.5\,kpc region.
Cross markers indicate positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (same as top right).
Modest smoothing has been applied to the maps. 
A divergent colormap is used for the Toomre $Q$ map to facilitate 
identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
Some MCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, whereas regions of $\log{Q_{\rm eff}}\lesssim0$ 
are likely gravitationally unstable.
\label{fig:Qeff}}
% \addtocounter{figure}{-1}
\end{figure*}
\clearpage

>>>>

Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in Figures~\ref{fig:Q}, \ref{fig:Qstar}, and \ref{fig:Qeff}, respectively. 
Before accounting for contribution of the stellar component to the gravitational potential, 
most MCs lie in regions of $\log{Q_{\rm gas}}\simeq$\,0 (see \Fig{Q}).
Fragmentation are expected in regions of low Toomre $Q_{\rm eff}$ values.
Further interpretation and implication of this is discussed in \Sec{origin}.

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_gas_toomre_proj_0_zoom_2.0_kpc}.png}
\caption{
Maps of the total gas surface density (top left), 
velocity dispersion (top right),
epicyclic frequency (bottom left), 
and Toomre $Q$ parameter (bottom right) in the $xy$-plane.
Modest smoothing has been applied to the maps. 
A divergent colormap is used for the Toomre $Q$ map to facilitate 
identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
Markers in the surface density and Toomre $Q$ maps
correspond to the mass-weighted positions of MCs identified using the lowest $n_{\rm cut}$. % using 0.32
Positions of sub-MCs identified using lower $n_{\rm cut}$ are not shown (but see top row of \Fig{Qeff} for an example). 
Before accounting for contribution of the stellar component to the 
gravitational potential, we find that most MCs lie in regions of 
$\log{Q_{\rm gas}}\simeq$\,0. 
\label{fig:Q}}
\addtocounter{figure}{-1}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=10 0 100 20, clip, width=0.35\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_0.32}.png}
\includegraphics[trim=30 0 10 20, clip, width=0.425\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_6.81}.png}  \\
\includegraphics[trim=10 0 0 10, clip, width=0.4\textwidth]{\figpath/{ss16_star_SD_proj_0_zoom_2.0_kpc}.png}  
\includegraphics[trim=10 0 0 10, clip, width=0.425\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_2.0_kpc}.png} \\
\includegraphics[trim=30 25 30 20, clip, width=0.38\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_0.8_kpc_6.81}.png} 
\includegraphics[trim=10 0 0 0, clip, width=0.38\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_0.8_kpc}.png}
\caption{
Effective two-component Toomre $Q_{\rm eff}$ (top row) 
and gas surface density (middle) maps projected onto the $xy$-plane.
Positions of MCs identified using the lowest $n_{\rm cut}$\eq0.32\,cm$^{-3}$ (top left; same as \Fig{Q})
and $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (top right) are overplotted as star markers.
Bottom row: Zoom-in view of the effective $Q_{\rm eff}$ (left) and gas surface density (right) maps.
Markers in the bottom left Toomre $Q$ map correspond to positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (same as top right).
Modest smoothing has been applied to the maps. 
A divergent colormap is used for the Toomre $Q$ map to facilitate 
identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
Some MCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, whereas regions of $\log{Q_{\rm eff}}\lesssim0$ 
are likely gravitationally unstable.
\label{fig:Qeff}}
% \addtocounter{figure}{-1}
\end{figure*}
\clearpage
